\cvsection{Experience}

\begin{cventries}
  \cventry
    {Machine Learning Engineering Intern}
    {Collins Aerospace}
    {Cedar Rapids, IA}
    {Jun. 2020 - Aug. 2020}
    {
      \begin{cvitems}
          \item {Designed and developed a modular sandbox environment for simulating resource management of radio antennas.}
          \item {Applied statistical techniques to synthesize datasets to mimic real world scenarios.}
          \item{Trained reinforcement learning agents in TensorFlow, to achieve highest performance for resource management.}
          \item{Utilized gpu server and TensorFlow docker to train models.}
          \item{Presented findings to contribute to the efforts of securing funding for further exploration.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern} % Job title
    {Nima Investments LLC} % Organization
    {Naperville, IL} % Location
    {Mar. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Automated creating monthly summary reports that are sent to investors using Python.}
        \item{Reduced time spent manually creating reports by 70\%}.
        \item{Developed a dashboard to display investor investment health status using Dash.}
      \end{cvitems}
    }
 
  \cventry
    {Reserach Leader} % Job title
    {CAM2 Human Behavior Team} % Organization
    {West Lafayette, IN} % Location
    {Aug. 2019 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed a re-identification system capable of identifying and re-identifying people across multiple cameras.}
        \item{Utilized a multi-granulated network that extracts features of a person to eliminate the need of storing identifiable information.}
        \item{Led development for a 2D mapping extension that condenses information into a map that displays the paths of each person across a timeline.}
      \end{cvitems}
    }
  
  \cventry
    {Intern} % Job title
    {FirstEigen} % Organization
    {Naperville, IL} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Integrated ML based data validation software into AWS.}
        \item{Published integrated software into the AWS marketplace}
      \end{cvitems}
    }

  \cventry
    {Research Leader} % Job title
    {Purdue University DURI} % Organization
    {West Lafayette, IN} % Location
    {Aug. 2018 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Analyzed and labeled 6000+ discussion forum comments to curate a dataset.}
        \item{Used to predict whether a comment has a significant impact to the discussion debate.}
      \end{cvitems}
    }
\end{cventries}
